Quantifying the home ground advantage

### 2020-03-19 inst/home_advantage.Rmd
copyedit

Thus ```home_games_won[1,2] == 16``` means A played at home against B
and won 16 times; ```home_games_won[2,1] == 19``` means B played at
home against A and won 19 times.  Also, ```away_games_won[1,2] == 5```
means A played away against B and won 5 times, and
```away_games_won[2,1] == 2``` means B played away against A and won 2
times.  Alternatively, A played B 16+19+5+2=45 times; A played at home
16+2=18 times and won 16 times and lost 2 times; and B played at home
19+5=24 times and won 19 times and lost 5 times.

@@

Now a likelihood ratio for the hypothesis that home strength (or home
advantage) is zero.  First define a function ```f()``` that maximises
the likelihood subject to the home strength being *less than* its
argument:

@@

See how the ```fcm``` and ```fcv``` constraints make the sum of
a,b,c,d, greater than ```1-home```.  Thus 'home' [which is the fillup
value, $p_\mathrm<{home}=1-(p_A+p_B+p_C+p_D)$] is constrained to be
less than argument ```home```.  Using this function, the likelihood
ratio test is straightforward:

>>>>

Thus `home_games_won[1,2] == 16` means A played at home against B and
won 16 times; `home_games_won[2,1] == 19` means B played at home
against A and won 19 times.  Also, `away_games_won[1,2] == 5` means A
played away against B and won 5 times, and `away_games_won[2,1] == 2`
means B played away against A and won 2 times.  Alternatively, A
played B 16+19+5+2=45 times; A played at home 16+2=18 times and won 16
times and lost 2 times; and B played at home 19+5=24 times and won 19
times and lost 5 times.

@@

Now a likelihood ratio for the hypothesis that home strength (or home
advantage) is zero.  First define a function `f()` that maximises the
likelihood subject to the home strength being *less than* its
argument:

@@

See how the `fcm` and `fcv` constraints make the sum of a,b,c,d,
greater than `1-home`.  Thus 'home' [which is the fillup value,
$p_\mathrm{home}=1-(p_A+p_B+p_C+p_D)$] is constrained to be less than
argument `home`.  Using this function, the likelihood ratio test is
straightforward:
